---
title: "Intro to Markdown"
author: "Luis Yasiel Colón Dávila" 
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output: 
  prettydoc::html_pretty: 
  theme: cayman
  highlight: github
---

```{css, echo=FALSE}
.page-header {
  background-image: none !important;
  background-color: #719052 !important;
}
body {
  background-color: #E1EFC2 !important;
}
```

# R Tutorials 2





```{r}

library(dplyr)
library(gapminder)

```

```{r}
data(gapminder)
head(gapminder)

```


## Q1. What class is the gapminder dataset? 

```{r}
class(gapminder)

```

## Q2. Filter a section of gapminder with a life expectancy smaller than 29. 

```{r}
gapminder %>%
  filter(lifeExp < 29)


```


## Q3 Filter the dataset for the country Rwanda and for years greater than 1979. 

```{r}
gapminder %>%
  filter(country == "Rwanda", year > 1979)


```


## Q4 Create a new dataset from gapminder excluding the column gdpPercap. 

```{r}
Ex_column <- gapminder %>% 
  select(country:pop)

Ex_column

```


## Q5 Arrange the dataset in ascending order of lifeExp.

```{r}
gapminder %>%
  arrange(lifeExp)


```


## Q6 Arrange the dataset in descending order of lifeExp. 

```{r}
gapminder %>%
  arrange(desc(lifeExp))


```


## Q7 Create a new dataset with only the columns year and lifeExp.

```{r}
LExp_set <- gapminder %>%
  select(lifeExp)

LExp_set


```


## Q8 Filter the dataset for the country Cambodia and show only the columns year and lifeExp. 

```{r}
gapminder %>%
  filter(country == "Cambodia") %>%
  select(year, lifeExp)


```


## Q9. Select only the countries in Africa.

```{r}
gapminder %>%
  filter(continent == "Africa") 


```


## Q10. Create a new column called lifeExp_months that shows life expectancy in months.

```{r}
lifeExp_months <- gapminder %>% 
  mutate(lifeExp_months = lifeExp * 12) 

lifeExp_months


```
